Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2016-06-09 manuscript-final.tex
Minor corrections from reading the galley proof

Previous work by \citet{Ku1977} investigated the use of the GLQ
in gravity forward modeling.
\citet{Ku1977} numerically integrated the vertical component of the
gravitational acceleration of right rectangular prisms.
The author suggested that the accuracy of the GLQ integration depends on
the ratio between distance to the computation point and the distance between
adjacent point masses.
Based on this, \citet{Ku1977} proposed an empirical criterion that
the distance between point masses should be greater than
the distance to the computation point.
\citet{Asgharzadeh2007} used  this criterion for the GLQ integration of
the gravity gradient tensor of tesseroids.
To our knowledge, an analysis of how well this ad hoc criteria of
\citet{Ku1977} works for gravity gradient components or for tesseroids
has never been done before.
There has also been no attempt to quantify the error committed in the GLQ
integration when applying the criteria of \citet{Ku1977}.

@@

Figure~4 shows
the maximum difference between the shell and tesseroid fields
as a function of $D$ for the four experiments.
The differences are given as a percentage of the shell value.
We established a maximum tolerated error of $0.1\%$, represented by the
horizontal solid lines in Figure~4.
Only results for the gravitational potential, $g_z$, and $g_{zz}$ are shown.
The results for the other diagonal components of the gravity gradient tensor
are similar to $g_{zz}$.
Figures for these components can be found in the supplementary material
(see section "Reproducing the analysis and results").

>>>>

Previous work by \citet{Ku1977} investigated the use of the GLQ
in gravity forward modeling.
\citet{Ku1977} numerically integrated the vertical component of the
gravitational acceleration of right rectangular prisms.
The author suggested that the accuracy of the GLQ integration depends on
the ratio between distance to the computation point and the distance between
adjacent point masses.
Based on this, \citet{Ku1977} proposed an empirical criterion that
the distance between point masses should not be greater than
the distance to the computation point.
\citet{Asgharzadeh2007} used  this criterion for the GLQ integration of
the gravity gradient tensor of tesseroids.
To our knowledge, an analysis of how well this ad hoc criteria of
\citet{Ku1977} works for gravity gradient components or for tesseroids
has never been done before.
There has also been no attempt to quantify the error committed in the GLQ
integration when applying the criteria of \citet{Ku1977}.

@@

Figure~4 shows
the maximum difference between the shell and tesseroid fields
as a function of $D$ for the four experiments.
The differences are given as a percentage of the shell value.
We established a maximum tolerated error of $0.1\%$, represented by the
horizontal solid lines in Figure~4.
Only results for the gravitational potential, $g_z$, and $g_{zz}$ are shown.
The results for the other diagonal components of the gravity gradient tensor
are similar to $g_{zz}$.
Figures for these components can be found in the supplementary material
(see section "Code for figures and error analysis").
